THESIS PROJECT PROPOSAL

### 2019-11-01 project_ashish/paper.tex
Update paper.tex

The production of Higgs boson in association with single top quark is one of the rare Higgs boson production mode. As the top 
quark is the heaviest fundamental particle in the standard model, due to its large mass, the top quark decay before 
hardronization which allow the possibility to reconstruct top quark from its decay products unlike the lighter quarks which 
undergo hardronization and are seen as bundles of particles in detector called jets. The most probable decay of top quark is into 
bottom (b) quark and W boson. Using b-jet tagging algorithms, the jet originating from b-quark can be reconstructed to identity 
the top quark. In SM, the coupling of the Higgs boson to fermions like quarks and leptons is proportional to the mass of the 
fermions. Thus heavy quarks like top, bottom and charm couple strongly to Higgs boson which means that out of all known quarks, 
top quark couple most strongly to the Higgs boson. So, it has a large value of Yukawa coupling y_t. That is why the Yukawa 
coupling of the top quark with the Higgs boson y_t has lot of importance as any deviation from standard model prediction might 
give an indication of new physics. The two processes at LHC which will allow us to directly probe the Yukawa coupling between 
Higgs Boson and top quark are Higgs boson production in association with top quark pair (t\bar{t} H) via strong interaction and 
the production of single top quark with a Higgs boson (tH). As tH occur via electroweak interaction, it is more rare than 
t\bar{t}H production. The Higgs boson in the tH channel can be radiated off by a W boson or by a top quark. These two processes 
in standard model have destructive interference which allow us to probe the relative sign between the coupling of top quark with 
Higgs boson y_t and the coupling of W boson to the Higgs boson. If the Yukawa coupling between top quark and Higgs boson y_t 
deviate from the SM prediction or even if y_t has a negative sign, both would cause a strong increase in the tH production cross 
section which is a special property of tH production channel making it an interesting production channel to probe using LHC 
2016, 2017 and 2018 data. The coupling strength modifier \kappa_t is defined as \kappa_t = \frac{y_t}{y^{SM}_t} which will tell us the 
deviation of y_t from the SM prediction.

@@

Aspects of simulation of signal production are studied based on generators that simulate the interactions of quarks and gluons taking 
into account the probability distributions of each type of particle. These are packages of software that are controlled with 
configuration files that define various aspects such as decay channels, energy in the center of mass and refinements in the development 
of the jets that are generated by the Strong interaction of the quarks. The reconstruction and selection of tH events requires the use 
of central software of the CMS collaboration. This software contains the algorithms that reconstruct the charged and neutral particles 
starting from the energy deposits in the different parts of the detector. These particles include leptons, photons and hadrons, 
whichThey have a life time that allows them to leave the interaction region. These particles are used to identify the production of the 
top and the Higgs. In the case of the top, it usually decays to a cuark b and a boson W. Subsequently the W decays to two Leptons or two 
quarks. Reconstruction requires finding a type b and two jet leptons. Improvements in this reconstruction can be done by studying the 
distributions of transverse momentum, the angular distributions of the different particles, and others properties.

>>>>

The production of Higgs boson in association with single top quark is one of the rare Higgs boson production mode. As the top 
quark is the heaviest fundamental particle in the standard model, due to its large mass, the top quark decay before 
hardronization which allow the possibility to reconstruct top quark from its decay products unlike the lighter quarks which 
undergo hardronization and are seen as bundles of particles in detector called jets. The most probable decay of top quark is into 
bottom (b) quark and W boson. Using b-jet tagging algorithms, the jet originating from b-quark can be reconstructed to identity 
the top quark. In SM, the coupling of the Higgs boson to fermions like quarks and leptons is proportional to the mass of the 
fermions. Thus heavy quarks like top, bottom and charm couple strongly to Higgs boson which means that out of all known quarks, 
top quark couple most strongly to the Higgs boson. So, it has a large value of Yukawa coupling y_t. That is why the Yukawa 
coupling of the top quark with the Higgs boson y_t has lot of importance as any deviation from standard model prediction might 
give an indication of new physics. The two processes at LHC which will allow us to directly probe the Yukawa coupling between 
Higgs Boson and top quark are Higgs boson production in association with top quark pair (t\bar{t} H) via strong interaction and 
the production of single top quark with a Higgs boson (tH). As tH occur via electroweak interaction, it is more rare than 
t\bar{t}H production. The Higgs boson in the tH channel can be radiated off by a W boson or by a top quark. These two processes 
in standard model have destructive interference which allow us to probe the relative sign between the coupling of top quark with 
Higgs boson y_t and the coupling of W boson to the Higgs boson. If the Yukawa coupling between top quark and Higgs boson y_t 
deviate from the SM prediction or even if y_t has a negative sign, both would cause a strong increase in the tH production cross 
section which is a special property of tH production channel making it an interesting production channel to probe using LHC 
2016, 2017 and 2018 data. The coupling strength modifier \kappa_t is defined as \kappa_t = \frac{y_t}{y^{SM}_t} will tell us the 
deviation of y_t from the SM prediction.

@@

Aspects of simulation of signal production are studied based on generators that simulate the interactions of quarks and gluons taking 
into account the probability distributions of each type of particle. These are packages of software that are controlled with 
configuration files that define various aspects of such as decay channels, energy in the center of mass and refinements in the development of the jets that are generated by the strong interaction of the quarks. The reconstruction and selection of tH events requires the use of central software of the CMS collaboration. This software contains the algorithms that reconstruct the charged and neutral particles starting from the energy deposits in the different parts of the detector. These particles include leptons, photons and hadrons which have a life time that allows them to leave the interaction region. These particles are used to identify the production of the top and the Higgs boson. In the case of the top quark, it usually decays to a bottom (b) quark and a W boson. Subsequently the W decays to two leptons or two quarks. Reconstruction requires finding a type b and two jet leptons. Improvements in this reconstruction can be done by studying the distributions of transverse momentum, the angular distributions of the different particles, and others properties.
